PS753 Glossary

### 2022-02-09 _academics/ps753-glossary/ps753-glossary.Rmd
text tweaks

two-mode data / bipartite data
: ties between different sets (or categories) of agents, such as ties between nations and international organizations

@@

>>>>

two-mode data / bipartite data
: ties between different sets (or categories) of agents, such as ties between nations and international organizations; a network split into two parts, each of whose nodes only connect to nodes in the opposite part, not to nodes within its own part

@@

average clustering coefficient
: the average of the local clustering coefficient of all nodes in the network
